---
title: "Stats and Plots"
author: "nick"
date: "3/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list=ls()) # clear the works pace of all data objects
ls() # list number of data objects in the work space
library(dplyr)
library(afex)
library(emmeans)
library(effectsize)
library(patchwork)
library(ggplot2)
#  may also need modelbased and PupillometryR packages for plotting
source("rain_ob_bg.R") #code for raincloud plots

# additional code for plots
this_theme <- theme(    
    panel.background    = element_blank() ,            #   control the major gridlines 
    panel.grid.major.y  = element_line() ,             #   suppress the vertical grid lines
    panel.grid.major.x  = element_blank() ,            #   suppress the minor grid lines
    panel.grid.minor    = element_blank() ,            #   add axes
    axis.text           = element_text(size=20, family="Times", colour='black'),   #   tick labels' size, font & color. 
    axis.line.x         = element_line( size=.8),   #   adjust the axis ticks
    axis.line.y         = element_line( size=.8),
    axis.ticks          = element_line( size=.8, colour='black'),   #   axis colors and thickness 
    axis.title.y        = element_text( angle=90, vjust= 1.5, hjust=.47,    
                                        size=20, family="Times"),  
    axis.title.x        = element_text(vjust=-.5, hjust = .505,                    
                                       size=20, family="Times"),                   
    plot.title = element_text (size=20, family="Times", colour='black', face = 'bold'),
    legend.text = element_text(size=20, family="Times"),
    legend.title = element_text(size=20, family="Times", face = 'bold'),
    plot.subtitle = element_text(size=20,  face="bold", color="black")
  )
```


```{r}
#setwd("") set working directory 
ndg_data_long    <- read.csv('memory_measures_data_longgraphs.csv',header = T)
ndg_arousal_long <- read.csv('arousal_data_long.csv',header = T)
```

```{r}
#Factor variables
vars_factor                   <- c("participant","study_instruction_condition","valence","scene_component")
vars_a_factor                 <- c("participant","study_condition")

ndg_data_long[vars_factor]    <- data.frame(lapply(ndg_data_long[vars_factor], factor))
ndg_arousal_long[vars_factor] <- data.frame(lapply(ndg_arousal_long[vars_a_factor], factor))

# clean up dataframes 
ndg_arousal_long <- arrange(ndg_arousal_long, participant, study_condition)
```
# OSF Hypothesis #1  | Hypothessis #3 for manuscript: 2 (valence: negative, neutral) X 2 (scene component: object, background) repeated measures ANOVA for the view trials. Follow up t-tests carried out for significant main effects or interactions.
```{r}
nd7_stat_h1 <- ndg_data_long%>%
  filter(study_instruction_condition == "view")%>% 
  droplevels()
#run model
nd7_aov_h1 <- aov_ez('participant','corrected_recognition',nd7_stat_h1,
                     within=c("valence","scene_component"),
                     anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_h1))
# Follow up t-tests

nd7_interaction2_h1    <- emmeans(nd7_aov_h1, "valence", by = c("scene_component"))
emto_pairs3_h2         <- summary(pairs(nd7_interaction2_h1, adjust = "none"))
emto_pairs2_es_h2      <- t_to_d(emto_pairs3_h2$t.ratio, emto_pairs3_h2$df, ci = .95)

#additional descriptives for means
emmeans(nd7_aov_h1, "valence")
emmeans(nd7_aov_h1, "scene_component")
```
# OSF Hypothesis # 2 | Manuscript #4 :  2 (study instruction: reappraise, view) x 2 (scene component: object, background) repeated measures ANOVA for decrease trials. Follow up t-tests will be carried out for significant main effects or interactions.
```{r}
study_remove_vars <- c("success","failure")

nd7_stat_h2 <- ndg_data_long%>%
  filter(valence == "negative",!study_instruction_condition %in% study_remove_vars)%>% 
  droplevels()
#run model
nd7_aov_h2 <- aov_ez('participant','corrected_recognition',nd7_stat_h2,
                     within=c("study_instruction_condition","scene_component"),
                     anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_h2))

# additional descriptives
emmeans(nd7_aov_h2, "scene_component")
emmeans(nd7_aov_h2, "study_instruction_condition")
emmeans(nd7_aov_h2, "study_instruction_condition", by = c("scene_component"))

#visualize
# set up dataframes
cr_df            <- modelbased::estimate_means(nd7_aov_h2)
cr_df$x_location <- c(.4,.6) + .1
cr_df_objects    <- cr_df%>%
  filter(scene_component == "objects")

df2_x_axis = nd7_stat_h2 %>%
  mutate(x_location = 
           case_when(study_instruction_condition == "decrease" ~.4,
                     study_instruction_condition == "view" ~.6)) %>%
  filter(scene_component == "objects")

# define plot features
sc_type        <- "Objects"
memory_measure <- "Corrected recognition" 
plot_colors    <- c("#3C5488FF", "#00A087FF") # colors for graph
x_break        <- c(.4,.6)
x_label        <- c("Decrease","View")
# Make the plots
rain_objects_reg <- make_cloud_plot(df2_x_axis, cr_df_objects,'corrected_recognition', memory_measure, plot_colors, x_break, x_label)

#backgrounds
cr_df_background <- cr_df%>%
  filter(scene_component == "background")
cr_df_background

df2_x_axis_bg <- nd7_stat_h2 %>%
  mutate(x_location = 
           case_when(study_instruction_condition == "decrease" ~.4,
                     study_instruction_condition == "view" ~.6)) %>%
  filter(scene_component == "background")

# Make the plots
memory_measure <- "Corrected recognition" 
sc_type        <- "Backgrounds"
rain_bg_reg    <- make_cloud_plot(df2_x_axis_bg, cr_df_background, 'corrected_recognition', memory_measure, plot_colors, x_break, x_label)

rain_objects_reg + rain_bg_reg
```
# OSF Hypothesis #3 | Manuscript # 5:  a 3 (reappraisal success: success, failure, view) x 2 (scene component: object, background) repeated measures ANOVA on corrected hits for negative scenes. Follow up t-tests will be carried out for significant main effects or interactions.
```{r}
study_remove_vars <- c("decrease","view_neutral")
nd7_stat_h3       <- ndg_data_long%>%
  filter(valence == "negative", !study_instruction_condition %in% study_remove_vars)%>% 
  droplevels()
#run model
nd7_aov_h3 <- aov_ez('participant','corrected_recognition',nd7_stat_h3,
                     within=c("study_instruction_condition","scene_component"),
                     anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_h3))
# Follow up t-tests
nd7_si_h3             <- emmeans(nd7_aov_h3, "study_instruction_condition")
emto_pairs_h3         <- summary(pairs(nd7_si_h3, adjust = "none"))
emto_pairs_es_h3      <- t_to_d(emto_pairs_h3$t.ratio, emto_pairs_h3$df, ci = .95)

nd7_interaction_h3    <- emmeans(nd7_aov_h3, "study_instruction_condition", by = c("scene_component"))
pairs_int             <- summary(pairs(nd7_interaction_h3, adjust = "none"))
emto_pairs_es_int     <- t_to_d(pairs_int$t.ratio, pairs_int$df, ci = .95)

# visualize 
# set up dataframes
cr_df            <- modelbased::estimate_means(nd7_aov_h3)
cr_df$x_location <- c(.4,.6,.8) + .1
cr_df_objects    <- cr_df%>%
  filter(scene_component == "objects")

df2_x_axis <- nd7_stat_h3 %>%
  mutate(x_location = 
           case_when(study_instruction_condition == "success" ~.6,
                     study_instruction_condition == "failure" ~.4,
                     study_instruction_condition == "view" ~.8)) %>%
  filter(scene_component == "objects")

# define plot features
sc_type        <- "Objects"
memory_measure <- "Corrected recognition" 
plot_colors    <- c("#DC0000FF", "#4DBBD5FF", "#00A087FF")
x_break        <- c(.4,.6,.8)
x_label        <- c("Failure","Success","View")
# Make the plots
rain_objects   <- make_cloud_plot(df2_x_axis, cr_df_objects,'corrected_recognition', memory_measure, plot_colors, x_break, x_label)

#backgrounds
cr_df_background <- cr_df%>%
  filter(scene_component == "background")

df2_x_axis_bg    <- nd7_stat_h3 %>%
  mutate(x_location = 
           case_when(study_instruction_condition == "success" ~.6,
                     study_instruction_condition == "failure" ~.4,
                     study_instruction_condition == "view" ~.8)) %>%
  filter(scene_component == "background")
# Make the plots
memory_measure <- "Corrected recognition" 
sc_type        <- "Backgrounds"
rain_bg        <- make_cloud_plot(df2_x_axis_bg, cr_df_background, 'corrected_recognition', memory_measure, plot_colors, x_break, x_label)

rain_objects + rain_bg
```
# OSF Hypothesis #4 | Manuscript #1: Paired t-test (study instruction: reappraisal vs view) for negative scenes. 
```{r}
arousal_vars_remove <- c("success","failure","view_neutral")
nd7_stat_h4         <- ndg_arousal_long %>%
  filter(!study_condition %in% arousal_vars_remove)%>% 
  droplevels()
#run model
nd7_aov_h4 <- aov_ez('participant','arousal_ratings',nd7_stat_h4,
                     within=c("study_condition"),
                     anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_h4))

nd7_h4             <- summary(pairs(emmeans(nd7_aov_h4, "study_condition")))
pairs_es_h4        <- t_to_d(nd7_h4$t.ratio, nd7_h4$df, ci = .95)
```
# OSF Hypothesis #5 | Manuscript #2:  a one way repeated measures ANOVA with the factor of reappraisal success (success, failure, view). If there is a significant main effect it will be followed up with paired t-tests (success vs. failure, success vs. view, failure vs. view).  
```{r}
study_remove_vars <- c("decrease","view_neutral")

nd7_stat_h5 <- ndg_arousal_long%>%
  filter(!study_condition %in% study_remove_vars)%>% 
  droplevels()
#run model
nd7_aov_h5 <- aov_ez('participant','arousal_ratings',nd7_stat_h5,
                     within=c("study_condition"),
                     anova_table = list(es = 'pes'))
knitr::kable(nice(nd7_aov_h5))
# Follow up t-tests
nd7_h5             <- emmeans(nd7_aov_h5, "study_condition")
pairs_h5           <- summary(pairs(nd7_h5, adjust = "none"))
pairs_es_h5        <- t_to_d(pairs_h5$t.ratio, pairs_h5$df, ci = .95)
```
