---
title: "ndg anova"
author: "nick"
date: "3/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
rm(list=ls()) # clear the workspace of all data objects
ls() # list number of data objects in the workspace
library(dplyr)
library(afex)
library(emmeans)
library(effectsize)
library(patchwork)
source("rain_ob_bg.R")
```

this_theme <- theme(    
    panel.background    = element_blank() ,            #   control the major gridlines 
    panel.grid.major.y  = element_line() ,             #   suppress the vertical grid lines
    panel.grid.major.x  = element_blank() ,            #   suppress the minor grid lines
    panel.grid.minor    = element_blank() ,            #   add axes
    axis.text           = element_text(size=20, family="Times", colour='black'),   #   tick labels' size, font & color. 
    axis.line.x         = element_line( size=.8),   #   adjust the axis ticks
    axis.line.y         = element_line( size=.8),
    axis.ticks          = element_line( size=.8, colour='black'),   #   axis colors and thickness 
    axis.title.y        = element_text( angle=90, vjust= 1.5, hjust=.47,    
                                        size=20, family="Times"),  
    axis.title.x        = element_text(vjust=-.5, hjust = .505,                    
                                       size=20, family="Times"),                   
    plot.title = element_text (size=20, family="Times", colour='black', face = 'bold'),
    legend.text = element_text(size=20, family="Times"),
    legend.title = element_text(size=20, family="Times", face = 'bold'),
    plot.subtitle = element_text(size=20,  face="bold", color="black")
  )
```{r}
setwd("C:/Users/nyeh/Desktop/fall_2021/NDG/exp1/data/analyses/")
ndg_data_long    <- read.csv('memory_measures_data_longgraphs.csv',header = T)
ndg_arousal_long <- read.csv('arousal_data_long.csv',header = T)
ndg_success      <- read.csv('reappraisal_strategy_success.csv',header = T)
df_ndg           <- read.csv('lme_data.csv',header = T)
df_ndg180        <- read.csv('lme180_data.csv',header = T)

nd007_alt_data   <- read.csv('tradeoff_datagraphs.csv',header = T)
# "sub-005","sub-015","sub-018",
bad_id = c("sub-031","sub-024","sub-038")
```

```{r}
#Factor variables
vars_factor                   <- c("participant","study_instruction_condition","valence","scene_component")
vars_a_factor                 <- c("participant","study_condition")

ndg_data_long[vars_factor]    <- data.frame(lapply(ndg_data_long[vars_factor], factor))
ndg_arousal_long[vars_factor] <- data.frame(lapply(ndg_arousal_long[vars_a_factor], factor))


ndg_success = ndg_success %>%
  filter(!participant %in% bad_id)%>% 
  select(success_total,participant)%>% 
  droplevels()


# clean up dataframes and merge 
ndg_data_long    <- inner_join(ndg_data_long,ndg_success, by = 'participant')
nd007_alt_data   <- inner_join(nd007_alt_data,ndg_success, by = 'participant')
ndg_arousal_long <- arrange(ndg_arousal_long, participant, study_condition)
nd007_alt_data   <- arrange(nd007_alt_data, participant ,study_instruction_condition )

temp_arousal     <- ndg_arousal_long %>%
  select(participant, study_condition, arousal_ratings, arousal_intact, arousal_ob, arousal_bg, arousal_f)%>%
  rename(study_instruction_condition = study_condition)

nd007_alt_data   <- inner_join(nd007_alt_data,temp_arousal, by = c('participant',"study_instruction_condition"))
```
# Hypothesis (replication) #1: 2 (valence: negative, neutral) X 2 (scene component: object, background) repeated measures ANOVA for the view trials. Follow up t-tests carried out for significant main effects or interactions.
```{r}
nd7_stat_h1 <- ndg_data_long%>%
  filter(study_instruction_condition == "view")%>% 
  droplevels()
#run model
nd7_aov_h1 <- aov_ez('participant','corrected_recognition',nd7_stat_h1,
                     within=c("valence","scene_component"),
                     anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_h1))
# Follow up t-tests
nd7_interaction_h1 <- emmeans(nd7_aov_h1, "scene_component", by = c("valence"))

emto_pairs         <- summary(pairs(nd7_interaction_h1, adjust = "none"))
emto_pairs_es      <- t_to_d(emto_pairs$t.ratio, emto_pairs$df, ci = .95)
```
# Hypothesis # 2:  2 (study instruction: reappraise, view) x 2 (scene component: object, background) repeated measures ANOVA for decrease trials. Follow up t-tests will be carried out for significant main effects or interactions.
```{r}
study_remove_vars <- c("success","failure")

nd7_stat_h2 <- ndg_data_long%>%
  filter(valence == "negative",!study_instruction_condition %in% study_remove_vars,!participant %in% bad_id)%>% 
  droplevels()
#run model
nd7_aov_h2 <- aov_ez('participant','corrected_recognition',nd7_stat_h2,
                     within=c("study_instruction_condition","scene_component"),
                     anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_h2))
# Follow up t-tests
nd7_si_h2             <- emmeans(nd7_aov_h2, "study_instruction_condition")
emto_pairs_h2         <- summary(pairs(nd7_si_h2, adjust = "none"))
emto_pairs_es_h2      <- t_to_d(emto_pairs_h2$t.ratio, emto_pairs_h2$df, ci = .95)

nd7_interaction_h2    <- emmeans(nd7_aov_h2, "study_instruction_condition", by = c("scene_component"))

#visualize
# set up dataframes
cr_df = modelbased::estimate_means(nd7_aov_h2)
cr_df$x_location <- c(.4,.6) + .1
cr_df_objects = cr_df%>%
  filter(scene_component == "objects")

df2_x_axis = nd7_stat_h2 %>%
  mutate(x_location = 
           case_when(study_instruction_condition == "decrease" ~.4,
                     study_instruction_condition == "view" ~.6)) %>%
  filter(scene_component == "objects")

# define plot featuers
sc_type <- "Objects"
memory_measure <- "Corrected recognition" 
plot_colors <- c("#3C5488FF", "#00A087FF") # colors for graph
x_break     <- c(.4,.6)
x_label     <- c("decrease","view")
# Make the plots
rain_objects_reg <- make_cloud_plot(df2_x_axis, cr_df_objects,'corrected_recognition', memory_measure, plot_colors, x_break, x_label)

#backgrounds
cr_df_background = cr_df%>%
  filter(scene_component == "background")
cr_df_background

df2_x_axis_bg = nd7_stat_h2 %>%
  mutate(x_location = 
           case_when(study_instruction_condition == "decrease" ~.4,
                     study_instruction_condition == "view" ~.6)) %>%
  filter(scene_component == "background")

# Make the plots
memory_measure = "Corrected recognition" #
sc_type = "Backgrounds"
#study_instruction_condition
rain_bg_reg <- make_cloud_plot(df2_x_axis_bg, cr_df_background, 'corrected_recognition', memory_measure, plot_colors, x_break, x_label)

rain_objects_reg + rain_bg_reg
```
#Hypothesis #3:  a 3 (reappraisal success: success, failure, view) x 2 (scene component: object, background) repeated measures ANOVA. Follow up t-tests will be carried out for significant main effects or interactions.
```{r}
study_remove_vars <- c("decrease","view_neutral")
nd7_stat_h3 <- ndg_data_long%>%
  filter(valence == "negative", !study_instruction_condition %in% study_remove_vars,!participant %in% bad_id)%>% 
  droplevels()
#run model
nd7_aov_h3 <- aov_ez('participant','corrected_recognition',nd7_stat_h3,
                     within=c("study_instruction_condition","scene_component"),
                     anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_h3))
# Follow up t-tests
nd7_si_h3             <- emmeans(nd7_aov_h3, "study_instruction_condition")
emto_pairs_h3         <- summary(pairs(nd7_si_h3, adjust = "none"))
emto_pairs_es_h3      <- t_to_d(emto_pairs_h3$t.ratio, emto_pairs_h3$df, ci = .95)

nd7_interaction_h3    <- emmeans(nd7_aov_h3, "study_instruction_condition", by = c("scene_component"))
pairs_int             <- summary(pairs(nd7_interaction_h3, adjust = "none"))
emto_pairs_es_int     <- t_to_d(pairs_int$t.ratio, pairs_int$df, ci = .95)
# visualize 
# set up dataframes
cr_df = modelbased::estimate_means(nd7_aov_h3)

cr_df$x_location <- c(.4,.6,.8) + .1
cr_df_objects = cr_df%>%
  filter(scene_component == "objects")

df2_x_axis = nd7_stat_h3 %>%
  mutate(x_location = 
           case_when(study_instruction_condition == "success" ~.6,
                     study_instruction_condition == "failure" ~.4,
                     study_instruction_condition == "view" ~.8)) %>%
  filter(scene_component == "objects")

# define plot featuers
sc_type <- "Objects"
memory_measure <- "Corrected recognition" 
plot_colors <- c("#DC0000FF", "#4DBBD5FF", "#00A087FF")
x_break     <- c(.4,.6,.8)
x_label     <- c("failure","success","view")
# Make the plots
rain_objects <- make_cloud_plot(df2_x_axis, cr_df_objects,'corrected_recognition', memory_measure, plot_colors, x_break, x_label)

#backgrounds
cr_df_background = cr_df%>%
  filter(scene_component == "background")

df2_x_axis_bg = nd7_stat_h3 %>%
  mutate(x_location = 
           case_when(study_instruction_condition == "success" ~.6,
                     study_instruction_condition == "failure" ~.4,
                     study_instruction_condition == "view" ~.8)) %>%
  filter(scene_component == "background")
# Make the plots
memory_measure = "Corrected recognition" 
sc_type = "Backgrounds"
#study_instruction_condition
rain_bg <- make_cloud_plot(df2_x_axis_bg, cr_df_background, 'corrected_recognition', memory_measure, plot_colors, x_break, x_label)

rain_objects + rain_bg
```
# Hypothesis #4: Paired t-test (study instruction: reappraisal vs view) for negative scenes. 
```{r}
arousal_vars_remove <- c("success","failure","view_neutral")

nd7_stat_h4 <- ndg_arousal_long %>%
  filter(!study_condition %in% arousal_vars_remove)%>% 
  droplevels()
#run model
nd7_aov_h4 <- aov_ez('participant','arousal_ratings',nd7_stat_h4,
                     within=c("study_condition"),
                     anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_h4))

nd7_h4             <- summary(pairs(emmeans(nd7_aov_h4, "study_condition")))
pairs_es_h4        <- t_to_d(nd7_h4$t.ratio, nd7_h4$df, ci = .95)
#decrease = ndg_arousal_long %>% filter(study_condition == "decrease")
#decrease = decrease$arousal_ratings

#view = ndg_arousal_long %>% filter(study_condition == "view_negative")
#view = view$arousal_ratings

#ttest = t.test(decrease,view)
```
Hypothesis #5:  a one way repeated measures ANOVA with the factor of reappraisal success (success, failure, view). If there is a significant main effect it will be followed up with paired t-tests (success vs. failure, success vs. view, failure vs. view).  
```{r}
study_remove_vars <- c("decrease","view_neutral")

nd7_stat_h5 <- ndg_arousal_long%>%
  filter(!study_condition %in% study_remove_vars)%>% 
  droplevels()
#run model
nd7_aov_h5 <- aov_ez('participant','arousal_ratings',nd7_stat_h5,
                     within=c("study_condition"),
                     anova_table = list(es = 'pes'))
knitr::kable(nice(nd7_aov_h5))
# Follow up t-tests
nd7_h5             <- emmeans(nd7_aov_h5, "study_condition")
pairs_h5           <- summary(pairs(nd7_h5, adjust = "none"))
pairs_es_h5        <- t_to_d(pairs_h5$t.ratio, pairs_h5$df, ci = .95)
```
#lme route
```{r}
bad_id_lme               <- c(24,31,38)

df_ndg                   <- df_ndg %>%
  filter(study_instruction != "NA",!id %in% bad_id_lme)%>% 
  droplevels()

df_ndg$study_instruction <- factor(df_ndg$study_instruction, levels = c("decrease","view"))
df_ndg$id                <- as.factor(df_ndg$id)
df_ndg$sc_image          <- as.factor(df_ndg$sc_image)
df_ndg$sc_type           <- as.factor(df_ndg$sc_type)
df_ndg$cb                <- as.factor(df_ndg$cb)
df_ndg$list              <- as.factor(df_ndg$list)

mixed_memory             <- mixed(test_item_resp~study_instruction*sc_type+(1|id)+ (1|sc_image),family = "binomial", method = "LRT" ,control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)),df_ndg)
mixed_memory 
memory_means             <- modelbased::estimate_means(mixed_memory)
memory_means

mixed_memory2            <- mixed(test_item_resp~study_success_resp*sc_type+(1+study_success_resp|id)+ (1|sc_image),family = "binomial", method = "LRT" ,control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)),df_ndg)

memory_means2            <- modelbased::estimate_means(mixed_memory2)
# Follow up test
emm_i1                   <- emmeans(mixed_memory2, "study_success_resp", by = "sc_type", type = "response")
#pairwise
summary(pairs(emm_i1), by=NULL, adjust = "none")

mb_pairs                 <- modelbased::estimate_contrasts(mixed_memory2, contrast = c("study_success_resp", "sc_type"), adjust = "none", transform = "response")

mixed_memory3            <- mixed(test_item_resp~study_success_resp*sc_type + study_arousal_resp + list + cb +(1+study_success_resp|id)+ (1|sc_image),family = "binomial", method = "LRT" ,control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)),df_ndg)
mixed_memory3
memory_means3            <- modelbased::estimate_means(mixed_memory3,at = c("study_success_resp", "sc_type"))
memory_means3
```
# alternative measures
```{r}
study_remove_vars         <- c("decrease","view_neutral")
#modify dataframe
nd7_stat_alt <- nd007_alt_data%>%
  filter(!study_instruction_condition %in% study_remove_vars,!participant %in% bad_id)%>% 
  droplevels()
#run Intact model
nd7_aov_alt <- aov_ez('participant','intact',nd7_stat_alt,
                      within=c("study_instruction_condition"),
                      anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_alt))
# Follow up t-tests
nd7_intact_pair           <- emmeans(nd7_aov_alt, "study_instruction_condition")
emto_pairs_results        <- summary(pairs(nd7_intact_pair, adjust = "none"))
emto_pairs_es_intact      <- t_to_d(emto_pairs_results$t.ratio, emto_pairs_results$df, ci = .95)

# run trade off model
nd7_aov_ob <- aov_ez('participant','OB',nd7_stat_alt,
                     within=c("study_instruction_condition"),
                     anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_ob))
# Follow up t-tests
nd7_ob_means              <- emmeans(nd7_aov_ob, "study_instruction_condition")
emto_pairs_ob             <- summary(pairs(nd7_ob_means, adjust = "none"))
emto_es_ob                <- t_to_d(emto_pairs_ob$t.ratio, emto_pairs_ob$df, ci = .95)
# run forget model
nd7_aov_forget <- aov_ez('participant','F',nd7_stat_alt,
                         within=c("study_instruction_condition"),
                         anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_forget))
# Follow up t-tests
nd7_forget_means          <- emmeans(nd7_aov_forget, "study_instruction_condition")
emto_pairs_forget         <- summary(pairs(nd7_forget_means, adjust = "none"))
emto_es_forget            <- t_to_d(emto_pairs_forget$t.ratio, emto_pairs_forget$df, ci = .95)
# run forget model
nd7_aov_bg<- aov_ez('participant','BG',nd7_stat_alt,
                    within=c("study_instruction_condition"),
                    anova_table = list(es='pes'))
knitr::kable(nice(nd7_aov_bg))
# Follow up t-tests
nd7_bg_means              <- emmeans(nd7_aov_bg, "study_instruction_condition")
emto_pairs_bg             <- summary(pairs(nd7_bg_means, adjust = "none"))
emto_es_bg                <- t_to_d(emto_pairs_bg$t.ratio, emto_pairs_bg$df, ci = .95)
```
#alternative LMES
```{r}
library(ggplot2)
library(see)
library(modelbased)
library(stringr)
bad_id_lme                  <- c(24,31,38)

df_ndg180                   <- df_ndg180 %>%
  filter(study_instruction != "NA",!id %in% bad_id_lme)%>% 
  droplevels()

ndg_success$id              <- as.numeric(str_remove(ndg_success$participant, "sub-"))
df_ndg180                   <- inner_join(df_ndg180, ndg_success, by = c('id'))

df_ndg180$study_instruction <- factor(df_ndg180$study_instruction, levels = c("decrease","view"))
df_ndg180$id                <- as.factor(df_ndg180$id)
df_ndg180$original_scene    <- as.factor(df_ndg180$original_scene)
df_ndg180$cb                <- as.factor(df_ndg180$cb)
df_ndg180$list              <- as.factor(df_ndg180$list)
df_ndg180$memory_type       <- as.factor(df_ndg180$memory_type)
df_ndg180$study_arousal_c   <- scale(df_ndg180$study_arousal_resp, scale=FALSE)

mixed_arousal180            <- mixed(study_arousal_resp~study_success_resp*memory_type+(1|id) + (1|original_scene),df_ndg180)
arousal_means180            <- modelbased::estimate_means(mixed_arousal180)
# 3. Plot
mixed2_memory180            <- mixed(Rearrange_OB~study_success_resp+(1|id) + (1|original_scene),df_ndg180)
memory2_means180            <- modelbased::estimate_means(mixed2_memory180)
mixed_memory180             <- mixed(Intact~study_success_resp+(1|id) + (1|original_scene),df_ndg180)
memory_means180             <- modelbased::estimate_means(mixed_memory180)
mixed_memory_type180        <- mixed(item_acc~study_success_resp+(1|id) + (1|original_scene),df_ndg180)
memory_means180             <- modelbased::estimate_means(mixed_memory180)
```

```{r}
library(tidyr)
nd007_alt_data$study_instruction_condition <- as.factor(nd007_alt_data$study_instruction_condition)
nd007_alt_data                             <- nd007_alt_data%>%
  mutate(failure_total = 60-success_total)

nd007_alt_data$arousal_ratings_center      <- scale(nd007_alt_data$arousal_ratings, scale=FALSE)
nd007_alt_data$arousal_ob_center           <- scale(nd007_alt_data$arousal_ob, scale=FALSE)

corr_data                                  <- nd007_alt_data%>%
  filter(study_instruction_condition %in% c("success","failure","view_negative"))%>% 
  droplevels()
# %>% drop_na()
cor(corr_data$tradeoff_index, nd007_alt_data$success_total, method = c("pearson", "kendall", "spearman"))
cor.test(corr_data$intact, corr_data$arousal_intact, method = c("pearson", "kendall", "spearman"), use = "complete.obs")

library("ggpubr")
library(ggplot2)
library("ggExtra")
library(cowplot) 
# Main plot

pmain <- ggscatter(corr_data, x = "arousal_ratings", y = "tradeoff_index", 
                  add = "reg.line", conf.int = TRUE, 
                  size = "success_total",
                  color = "study_instruction_condition", palette = "jco",
                  cor.coef = TRUE, cor.method = "pearson",
                  xlab = "arousal rating resp", ylab = "trade-off")+
  stat_cor(aes(color = study_instruction_condition), label.x = 3)  +
  ggtitle("") + 
  theme(legend.title=element_blank(),legend.position = "bottom")

# Marginal densities along x axis
xdens <- axis_canvas(pmain, axis = "x")+
  geom_density(data = corr_data, aes(x = arousal_ratings, fill = study_instruction_condition),
               alpha = 0.7, size = 0.2)+
  ggpubr::fill_palette("jco")
# Marginal densities along y axis
# Need to set coord_flip = TRUE, if you plan to use coord_flip()
ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE)+
  geom_density(data = corr_data, aes(x = tradeoff_index, fill = study_instruction_condition),
               alpha = 0.7, size = 0.2)+
  coord_flip()+
  ggpubr::fill_palette("jco")
p1 <- insert_xaxis_grob(pmain, xdens, grid::unit(.2, "null"), position = "top")
p2<- insert_yaxis_grob(p1, ydens, grid::unit(.2, "null"), position = "right")
ggdraw(p2)

p2_lme           <- mixed(OB~study_instruction_condition*arousal_ob_center+success_total+(1|participant),corr_data)
memory2_means180 <- modelbased::estimate_means(p2_lme)

p2_lme           <- mixed(Rearrange_OB~study_success_resp*study_arousal_resp*success_total+(1+study_success_resp|id)+ (1|original_scene),
                 control = lmerControl(optimizer="bobyqa", optCtrl = list(maxfun=100000)),df_ndg180)
p2_lme_means180  <- modelbased::estimate_means(p2_lme)

parameters::model_parameters(lm(formula = intact ~ arousal_intact, data = corr_data))

lm_model = lm(tradeoff_index ~ study_instruction_condition * success_total, data = corr_data)
cooksd <- cooks.distance(lm_model)
plot(cooksd, pch="*", cex=2, main="Influential Obs by Cooks distance")  # plot cook's distance
abline(h = 4*mean(cooksd, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksd)+1, y=cooksd, labels=ifelse(cooksd>4*mean(cooksd, na.rm=T),names(cooksd),""), col="red")
influential <- as.numeric(names(cooksd)[(cooksd > 4*mean(cooksd, na.rm=T))])  # influential row numbers
head(corr_data[influential, ])
```

```{r regression and rain}
pmain      <- ggscatter(corr_data, x = "arousal_intact", y = "intact", 
                        add = "reg.line", conf.int = TRUE, 
                        size = "success_total",
                        color = "study_instruction_condition", palette = COLOR_TEMP,
                        cor.coef = TRUE, cor.method = "pearson",
                        xlab = "arousal rating resp", ylab = "trade-off")+
  scale_size(range = c(1, 10), name="Reappraisal success")+
  stat_cor(aes(color = study_instruction_condition), label.x = 3)  +
  ggtitle("")+
  this_theme+ 
  theme(legend.position = "bottom")
pmain      <- ggpar(pmain, xlim = c(1,6), ylim = c(0,1), xticks.by = 1,
                    legend.title = list(color = "", fill = "", size = ""),
                    font.legend = c(14, "plain", "black"))
pmain

COLOR_TEMP <- c("#d5896f","#70a288","#dab785")

c_main_p   <- ggplot(corr_data, aes(x = arousal_intact, y = intact))
main_p     <- c_main_p +
  geom_point(aes(color = study_instruction_condition,
                 size = success_total),
             alpha = 0.25, stroke = 0.7) +
  geom_smooth(aes(color = study_instruction_condition),
              formula = 'y ~ x',
              method = "lm") +
  scale_y_continuous(name = "Trade-off", 
                     limits = c(0, 1), expand = c(0, 0)) + 
  scale_x_continuous(name = "arousal rating resp", 
                     limits = c(1, 6), expand = c(0, 0))+
  scale_fill_manual(values = COLOR_TEMP) +
  scale_color_manual(values = COLOR_TEMP,labels = c("failure","success","view")) +
  labs(x = "arousal", y = 'trade-off', title = '')+
  this_theme + 
  theme(legend.title=element_blank(),legend.position = "bottom")

y_rain     <- ggplot(corr_data, aes(y = intact, x = study_instruction_condition, fill = study_instruction_condition)) +
  PupillometryR::geom_flat_violin(position = position_nudge(x = .2), alpha = .8) +
  geom_point(aes(color = study_instruction_condition), 
             position = position_jitter(width = .15),
             size = .3, alpha = .5, show.legend = F) +
  geom_boxplot(width = .3, outlier.shape = NA, alpha = .5) +
  labs(x = "", y = "") +
  scale_fill_manual(values = COLOR_TEMP, guide = "none") +
  scale_color_manual(values = COLOR_TEMP,) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) + 
  scale_x_discrete(labels = c("failure","success","view")) +
  this_theme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, color = COLOR_TEMP))

x_rain     <- ggplot(na.omit(corr_data),
                     aes(y = arousal_intact,
                         x = study_instruction_condition, fill = study_instruction_condition)) +
  PupillometryR::geom_flat_violin(position = position_nudge(x = .2), alpha = .8) +
  geom_point(aes(color = study_instruction_condition), position = position_jitter(width = .15),
             size = 1, alpha = .5, show.legend = F) +
  geom_boxplot(width = .3, outlier.shape = NA, alpha = .5) +
  labs(x = "", y = "", fill = NULL) +
  scale_fill_manual(values = COLOR_TEMP, guide=FALSE) +
  scale_color_manual(values = COLOR_TEMP) + 
  scale_x_discrete(labels = c("failure","success","view"))+
  scale_y_continuous(limits = c(1, 6), expand = c(0, 0),labels = c("1","2","3","4","5","6")) +
  coord_flip() +
  this_theme +
  theme(axis.text.y = element_text( color = COLOR_TEMP))

intact_p + plot_annotation(
  title = 'Remembering whole scenes (reduced trade-off?)',
  subtitle = '',caption = ''
)
to_index + plot_annotation(
  title = 'Trade-off index (Objects - Backgrounds)',
  subtitle = '',caption = ''
)
alt_ob + plot_annotation(
  title = 'Whole scene trade-off (R: ob, F: bg)',
  subtitle = '',caption = ''
)

intact_p <- x_rain + plot_spacer() + pmain + y_rain + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))

to_index <- x_rain + plot_spacer() + pmain + y_rain + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))

alt_ob   <- x_rain + plot_spacer() + pmain + y_rain + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))

alt_ob
```
#examine reappraisal success
```{r}
library(smplot)
library(gganimate)

df_ndg180 <- df_ndg180%>%
  mutate(success_coded  = case_when(
    study_success_resp == 'success' ~ 1,
    study_success_resp == 'failure' ~ 0
    # view trials are NA
  ))

# block order
df_ndg180$block_number <- as.factor(df_ndg180$block_number)

sm_test <- df_ndg180%>%
  select(id,study_instruction,block_number,success_coded)%>%
  filter(study_instruction != 'view')%>%
  group_by(id,block_number)%>%
  summarise(avg_success_block = mean(success_coded))

sm_test$block_renum <- rep(1:6, times = 40)
sm_test$id <- as.factor(sm_test$id)

block_plot <- sm_raincloud(data = sm_test, x = as.factor(block_renum), y = avg_success_block,
             boxplot_alpha = 0.5, color = 'white', shape = 21, sep_level = 3) +
  scale_x_continuous(limits = c(0,7), labels = c('1', '2', '3', '4','5', '6'), breaks = c(1,2,3,4,5,6)) +
  scale_y_continuous(limits = c(.3,1.05), breaks = c(.4,.6,.8,1)) +
  xlab('Block order')+
  ylab('success rate')+
  scale_color_manual(values = rep('transparent',6)) + 
  scale_fill_manual(values = sm_palette(6))

block_plot <- block_plot+
  labs(title = 'Time: {frame_time}', x = 'Blocks', y = 'Reappraisal success') +
  transition_time(block_renum) +
  ease_aes('linear')



block_plot+ 
  transition_states(block_renum,
                    transition_length = 2,
                    state_length = 1)+ 
  enter_fade() + enter_drift(x_mod = -1) + 
#  exit_shrink() + exit_drift(x_mod = 5)+ 
  ggtitle('Now showing {closest_state}',
          subtitle = 'Frame {frame} of {nframes}')

block_plot

# block trial 
sm_bt2 <- df_ndg180%>%
  select(id,study_instruction,block_trial,success_coded)%>%
  filter(study_instruction != 'view')%>%
  group_by(id,block_trial)%>%
  summarise(avg_success_block = mean(success_coded))
#sm_bt$block_renum <- rep(1:6, times = 37)

trial_plot <- sm_raincloud(data = sm_bt2, x = as.factor(block_trial), y = avg_success_block,
             boxplot_alpha = 0.5, color = 'white', shape = 21, sep_level = 4 , jitter_width =  .1) +
  scale_x_continuous(limits = c(0,11), labels = c('1', '2', '3', '4','5', '6','7','8','9','10'), breaks = c(1,2,3,4,5,6,7,8,9,10)) +
  scale_y_continuous(limits = c(.3,1.05), breaks = c(.4,.6,.8,1)) +
  xlab('Block trial order')+
  ylab('success rate')+
  scale_color_manual(values = rep('transparent',10)) + 
  scale_fill_manual(values = sm_palette(10))

trial_plot + transition_states(block_trial, wrap = FALSE) +
  shadow_mark()+ 
  enter_fade() + enter_drift(x_mod = -1) + 
#  exit_shrink() + exit_drift(x_mod = 5)+ 
  ggtitle('Now showing {closest_state}',
          subtitle = 'Frame {frame} of {nframes}')



  transition_states(block_trial,
                    transition_length = 4,
                    state_length = 2)+ 
  enter_fade() + enter_drift(x_mod = -1) + 
#  exit_shrink() + exit_drift(x_mod = 5)+ 
  ggtitle('Now showing {closest_state}',
          subtitle = 'Frame {frame} of {nframes}')

anim_save("test", animation = last_animation())

```

```{r}
# We'll start with a static plot
p <- ggplot(iris, aes(x = Petal.Width, y = Petal.Length)) + 
  geom_point()

plot(p)

anim <- p + 
  transition_states(Species,
                    transition_length = 2,
                    state_length = 1)

anim
```

